---
title: "Technology Gobbledygook Generator"
author: "Thomas Speidel"
date: "06/08/2018"
output: html_document
---


```{r setup, include=FALSE}
#-----------------------------------------------------------------------------------------#
# SET COMMON OPTIONS
#-----------------------------------------------------------------------------------------#
library(knitr)
library(rmdformats)

options(max.print="75")

knitr::opts_chunk$set(dev='png', 
                      echo = TRUE, 
                      warning=FALSE, 
                      message=FALSE, 
                      fig.path = 'Figures/', 
                      strip.white = TRUE, 
                      dpi = 144)

knitr::opts_knit$set(eval.after = 'fig.cap')
knitr::opts_knit$set(width=75)

#-----------------------------------------------------------------------------------------#
# SET PRETTY LOOKING NUMBERS
#-----------------------------------------------------------------------------------------#
knitr::knit_hooks$set(inline = function(x) {
      if(is.numeric(x)){
          return(prettyNum(x, big.mark=","))
      }else{
          return(x)
       }
   })


```


```{r, eval=TRUE,  message=FALSE}
#-----------------------------------------------------------------------------------------#
# NEEDED PACKAGES
#-----------------------------------------------------------------------------------------#
library(markovifyR)
library(markovchain)
library(dplyr)
library(tidytext)
library(tidyverse)
library(tm)
library(purrr)
library(stringr)
library(textclean)
library(kableExtra)
library("extrafont")

# font_import(pattern="[O/o]swald")
# font_import(pattern="PT_Sans")
# font_import(pattern="[R/r]aleway")
# loadfonts(device="win")

# system("pip install markovify")
# devtools::install_github("abresler/markovifyR")
## https://github.com/abresler/markovifyR

```




Much hype is generated from technology consulting firms and vendors. This has led firms like Gartner to publish the now popular ???[Hype Cycle](https://en.wikipedia.org/wiki/Hype_cycle)???.

This is a **humorous collection** of (loosely) convincing sentences I generated based on training data found on the website of 5 popular technology vendor and consulting firms. Of course, the selection of the training data is biased, as I only looked for areas where buzzwords are common. 

The generator uses a [Markov chain](https://en.wikipedia.org/wiki/Markov_chain), a true random process model, not another meaningless term.


```{r, eval=TRUE, message=FALSE}

## Load data
# cname <- file.path("F:/GoogleDrive/Personal_Work/Gibberish_Generator/Data")

cname <- file.path("/home/tspeidel/GoogleDrive/Personal_Work/Gibberish_Generator/Data")

docs <- VCorpus(DirSource(cname))
docs <-data.frame(text = unlist(sapply(docs, `[`, "content")), stringsAsFactors = F)


## Cleanup
docs <- docs %>%
  filter(cumsum(text == "") > 0,
         cumsum(str_detect(text, "^--")) == 0) %>%
  drop_empty_row() %>%
  tibble::rowid_to_column("id")

docs$text <- strip(docs$text, char.keep = c("?", ",", ";", "."))
docs$text <- replace_contraction(docs$text)
docs$text <- replace_html(docs$text)
docs$text <- replace_non_ascii(docs$text)
docs$text <- replace_number(docs$text, remove=TRUE)
docs$text <- replace_symbol(docs$text)
docs$text <- replace_white(docs$text)



## Markov model
buzz <- docs %>% pull(text)

markov_model <-
  generate_markovify_model(
    input_text = buzz,
    markov_state_size = 2L,
    max_overlap_total = 25,
    max_overlap_ratio = .85
  )


buzz.out <- markovify_text(
  markov_model = markov_model,
  maximum_sentence_length = NULL,
  output_column_name = "Gibberish",
  count = 30,
  tries = 200,
  only_distinct = TRUE,
  return_message = FALSE
)

kable(buzz.out, "html", align = "l", digits = 1) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F, position = "left")
  
```



